---
title: "My title"
header-includes:
   - \usepackage{comment}
   - \usepackage[spanish]{babel}
   - \usepackage[utf8]{inputenc} 
   - \usepackage{hyperref}
   - \usepackage{multicol}
   - \usepackage{tocloft}
   - \usepackage{float}
   - \usepackage{graphicx}
   - \usepackage{lipsum}
documentclass: article
classoption: twoside
output: 
  pdf_document:
    fig_caption: true
graphics: yes
---


\begin{comment}
-----------------------------------------------------------------------
=======================================================================
-----------------------------------------------------------------------
\end{comment}

\setlength{\columnsep}{0.55cm}
\setlength{\fboxrule}{0.75pt}

\definecolor{color1}{RGB}{0,0,90}

\hypersetup{linkcolor=color1}

\flushbottom

\setcounter{secnumdepth}{5}

\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}

\renewcommand\tablename{Tabla}

\setcounter{tocdepth}{1}

\renewcommand{\contentsname}{Contenido}

```{r echo=FALSE}
library(ggplot2)

```

\begin{comment}
-----------------------------------------------------------------------
=======================================================================
-----------------------------------------------------------------------
\end{comment}

\begin{center}

My subtitle \\

\vspace{10mm}

Author 1 \\
Author 2 \\
\vspace{5mm}
Course \\
Program \\
Faculty - University\\
Year \\
\end{center}

\begin{center}
\section*{Abstract}
\end{center}

\lipsum[3]

\vspace{10mm}

\begin{multicols}{2}

\tableofcontents


\section*{Introducción}
\addcontentsline{toc}{section}{Introducción}

\lipsum[1]

\section{My section}

\lipsum[2]

\subsection{My subsection}

\lipsum[4]

\end{multicols}


```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE, tidy=TRUE}

my.data <- mpg

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE, fig.cap="Gráfico ejemplo de ggplot.",  fig.height=5, fig.width=10}
ggplot(my.data, aes(x=manufacturer,fill=class)) + geom_bar() + scale_fill_brewer(palette = "Set1") + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

\begin{multicols}{2}

\lipsum[5]

\end{multicols}


\newpage

\begin{center}
\section*{Apéndice}
\addcontentsline{toc}{section}{Apéndice}
\end{center}


\includegraphics{example}
\begin{center}
Figura A1. Gráfico externo de ejemplo.
\end{center}

\begin{multicols}{2}

\begin{thebibliography}{99}
\addcontentsline{toc}{section}{Referencias}

\bibitem{MWE1} Merriam-Webster, «Merriam-Webster, Incorporated,» 2016. [En línea]. Available: \url{http://www.merriam-webster.com/dictionary/network}. [Último acceso: 26 Abril 2016].

\end{thebibliography}

\end{multicols}



